\section{Introduction} 
%---------------------------------------------------------
%Changing visivility of the text
\begin{frame}
\frametitle{Brief Definition and History of Computers}
\begin{exampleblock}{Definition}
	What is a Computer: is programmable electronic device that accepts raw data as input and processes it with a set of instructions (a program) to produce the result as output. It was derived from the Latin word which means, "Compute" - which means to calculate. 
\end{exampleblock}
\begin{large}
	\textbf{History of Computers.}
\end{large}

Generally speaking, computers can be classified into three generations\\
\begin{itemize}
	\item [First generation : 1937 – 1946]
		\begin{itemize}
			\item Developement of the ABC Computer by Developed Dr. John V. Atanasoff and Clifford Berry
			\item 1943 Computer name the Colossus was built for the military
			\item 1946 Electronic Numerical Integrator and Computer (ENIAC) was built
		\end{itemize}
	\item [First generation : ]
\end{itemize}


First generation: 1937 – 1946. Developed Dr. John V. Atanasoff and Clifford Berry and was called called the Atanasoff-Berry Computer (ABC). In 1943 an electronic computer name the Colossus was built for the military. Other developments continued until in 1946 the first general– purpose digital computer, the Electronic Numerical Integrator and Computer (ENIAC) was built.

Second generation: 1947 – 1962 - This generation of computers used transistors instead of vacuum tubes which were more reliable. In 
1951 the first computer for commercial use was introduced to the public; the Universal Automatic Computer (UNIVAC 1). In 1953 the International Business Machine (IBM) 650 and 700 series computers made their mark in the computer world. During this generation of computers over 100 computer programming languages were developed, computers had memory and operating systems. Storage media such as tape and disk were in use also were printers for output.

Third generation: 1963 - present - The invention of integrated circuit brought us the third generation of computers. With this invention computers became smaller, more powerful more reliable and they are able to run many different programs at the same time. In 1980 Microsoft Disk Operating System (MS-Dos) was born and in 1981 IBM introduced the personal computer (PC) for home and office use. Three years later Apple gave us the Macintosh computer with its icon driven interface and the 90s gave us Windows operating system.

As a result of the various improvements to the development of the computer we have seen the computer being used in all areas of life. It is a very useful tool that will continue to experience new development as time passes.
\end{frame}
